%!TEX root = main.tex
\section{General Form}
The alphabet of a \textit{ternary labelling problem} is $\Sigma = \{0,1,2\}$\\\\
A \textit{ternary labelling problem} is a tuple $\Pi = (\wdd,\bdd,W,B)$ where :
\begin{itemize}
    \item $\wdd\in\{2,3,...\}$ is the \textit{white degree}
    \item $\bdd\in\{2,3,...\}$ is the \textit{black degree}
    \item $W$ is the \textit{white constraint}, a set of \textit{white configurations}
    \item $B$ is the \textit{black constraint}, a set of \textit{black configurations}
\end{itemize}
Each \textit{white configuration} is a 3-tuple $(x_1,x_2,x_3)$ where $x_1+x_2+x_3 = \wdd$\\
Each \textit{black configuration} is a 3-tuple $(x_1,x_2,x_3)$ where $x_1+x_2+x_3 = \bdd$\\\\
The problem is solved correctly if :
\begin{itemize}
    \item Each edge is labelled with some label $l\in\Sigma$
    \item For each white, resp. black, node, the tuple $(x_1,x_2, x_3)$, with $x_i$ the number of incident edges labelled with the label $i$, is a configuration contained in W, resp. B
\end{itemize}

\section{Alpha Form}
The general form presented above has been chosen as the internal form of a problem in the classifier, however, we can describe a problem $\Pi$ in a more readable form using regular expressions \cite{1,LB_MM} to represent the sets of configurations (constraints).
\begin{itemize}
    \item $\wdd\in\{2,3,...\}$ is the \textit{white degree}
    \item $\bdd\in\{2,3,...\}$ is the \textit{black degree}
    \item $W$ is the \textit{white constraint}, a set of \textit{white configurations}
    \item $B$ is the \textit{black constraint}, a set of \textit{black configurations}
\end{itemize}
Each \textit{white configuration}  and \textit{black configuration} is a multiset containing exactly $\wdd$ (resp. $\bdd$) labels (not necessarily distinct) from $\Sigma$ also know as regular expressions\\\\
The problem is solved correctly if :
\begin{itemize}
    \item Each edge is labelled with some label $l\in\Sigma$
    \item For each white, resp. black, node, the tuple $(x_1,x_2, ..., x_k)$ (with $k=\wdd$, resp. $k=\bdd$) of incident edges labels is a configuration contained in W, resp. B.
\end{itemize}
We also use the following notations for defining configurations :
\begin{itemize}
    \item $[x_1x_2,...x_k] = x1|x_2|...|x_k$
    \item $x^k$ for x repeated k times
\end{itemize}
\begin{exmp}
(maximal-Matching). The maximal matching problem for $\Delta = \wdd = \bdd = 3$ can be described in the alpha form as :
\begin{itemize}
    \item $W = MO^{2}|P^{3}$
    \item $B = M[OP]^{2}|O^{3}$
\end{itemize}
We can then describe the problem using the general form as
$\Pi = (3,3,W,B)$ with :
\begin{itemize}
    \item $W = \{(0,0,3),(1, 2, 0)\}$
    \item $B = \{(0,3,0),(1,2,0),(1,1,1),(1,0,2)\}$
\end{itemize}
(we did here the following mapping : $M\rightarrow 0, O\rightarrow 1, P\rightarrow 2$)
\end{exmp}
\section{The nodes-as-edges notation}
When $\bdd = 2$, one could find an equivalent problem $\Pi'$ to $\Pi = (\wdd,2,W,B)$ on a bipartite graph $G$ using the following idea \cite{1}:

The graph $G'$ is G where all black nodes are edges. This lead $G'$ to be exclusively composed of white nodes where only the ones with a degree $\wdd$ are considered by $\Pi'$.
$\Pi'$ acts as the following on the graph $G'$ instead of $G$:\\
Each of its must labels their ports according to $W$ and, for every two such nodes $u$ and $v$, if there is an edge between them, the 2 labels of the corresponding ports must be in $B$\\

\section{Alphabets}
The alphabet of the white constraint of a given problem $\Pi$ is the subset of the labels used in all white configurations, we denote it $A_{\Pi,w}$. Similarly, the alphabet of the black constraint is denoted $A_{\Pi,b}$\\\\
The effective alphabet of a problem is the union between the alphabet of the white constraint and the one of the black constraint $A_{\Pi} = A_{\Pi,w} \cup A_{\Pi,b} \subseteq \Sigma$. It correspond to the labels used by the problem.
\begin{exmp}
Let $\Pi = (2,3,W,B)$ with :
\begin{itemize}
    \item $W = \{(0,0,2)\}$
    \item $B = \{(0,0,3),(0,2,1)\}$
\end{itemize}
The white alphabet is $\{3\}$, the black alphabet is $\{2,3\}$, the effective alphabet is then $\{2,3\}$
\end{exmp}
\section{Equivalence}
%TODO CHANGE EXAMPLE NUMBER TO LABELS
Using the notation introduced in 1.0.1 and 1.0.2, a problem can have multiple representations, depending on the mapping that is done. Thus, this subsection states the conditions for two representations of a problem to be equivalent.\\\\
If X is a set of 3-tuples $(x_1,x_2, x_3)$, we denote $X_{a,b,c}$ the set that contains all the 3-tuples $(x_a,x_b, x_c)$ such that $(x_1,x_2, x_3)\in X$;  $a,b,c$ being a permutation of $(1,2,3) $.\\\\
The following problems have the same complexity up to +/- 1 round : 
\begin{itemize}
    \item $\Pi_0 = (\wdd,\bdd,W,B)$
    \item $\Pi_1 = (\bdd,\wdd,B,W)$
    \item $\Pi_2 = (\wdd,\bdd,W_{a,b,c},B_{a,b,c})$
    \item $\Pi_3 = (\bdd,\wdd,B_{a,b,c},W_{a,b,c})$
\end{itemize}
with $a,b,c \in permutations(1,2,3)$
\begin{exmp}
The following problem with $\wdd = 2$ and $\bdd = 3$ :
\begin{itemize}
    \item $W = BC|AA$
    \item $B = B(CC|BA|BC)$
\end{itemize}
Can be described as :
$\Pi = (2,3,W,B)$ with $(W,B)$ or $(B,W)$ being one of the following tuples:\\\\
\begin{array}{cc}
    $( \{(0,1,1),(2, 0, 0)\}$ &  $\{(0,1,2),(1,2,0),(0,2,1)\} )$\\
    $( \{(1,0,1),(0, 2, 0)\}$ &  $\{(2,0,1),(0,1,2),(1,0,2)\} )$\\
    $( \{(1,1,0),(0, 0, 2)\}$ &  $\{(1,2,0),(2,0,1),(2,1,0)\} )$\\
    $( \{(0,1,1),(2, 0, 0)\}$ &  $\{(0,2,1),(1,0,2),(0,1,2)\} )$\\
    $( \{(1,0,1),(0, 2, 0)\}$ &  $\{(1,0,2),(2,1,0),(2,0,1)\} )$\\
    $( \{(1,1,0),(0, 0, 2)\}$ &  $\{(2,1,0),(0,2,1),(1,2,0)\} )$
\end{array}
\end{exmp}
\section{Representative problem}
The representative problem $\Pi_c$ of set of equivalent problems will be used to represent them all in order to reduce the database size. The representative problem is found by sorting each of the white and black lists of configurations of the problems in the equivalent list, by alpha-numerical order. Then the whole equivalent list is sorted and the first problem is the representative problem.
\begin{exmp}
Considering the previous example,
\end{exmp}
\section{Restrictions, Relaxations}
A problem $\Pi_1 = (\wdd,\bdd,W_1,B_1)$ is a \textit{restriction} of a problem $\Pi_2 = (\wdd,\bdd,W_2,B_2)$ (and $\Pi_2$ is a relaxation of $\Pi_1$) if and only if $W_1\subseteq W_2$ and $B_1\subseteq B_2$